---
title: "Run simulations for each scenario"
output: pdf_document
date: "2023-10-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(miceadds)
library(infinitefactor)
library(bkmr)
library(horseshoe)
library(rstan)
source.all(path="R")
source("R/infinitefactor/R/interactionDL.R")
```


# Section 4 simulations

The first block of code below runs 100 replications of the simulations in Section 4.

Then, the remaining code blocks summarize the already-completed simulations stored 
in the simulations_results directory, which we ran in parallel on the Duke Compute
Cluster for use in the paper. (These summary chunks can be run without running the
first block.)



## Run all simulations in a loop

NOTE: This code chunk would take a very long time (i.e., weeks) to run sequentially.

```{r}
# Note: The initial run of LowFR for seed 11, scenario 3 had some convergence
# issues, so the result in the simulations_results folder are for a second run
# with the Stan parameter init_r set to 0.2.
scenario_list <- 1:3
seed_list <- 1:100
for (scenario in scenario_list) {
  for (i in seed_list) {
    start_time <- Sys.time()
    print(paste0("Scenario ", scenario, " seed ", i, " simulations started at ", start_time, "."))
    
    LowFR_sim <- run_sim_LowFR(scenario=scenario,
                save_output=TRUE,
                #path=paste0("simulations/LowFR/scenario", scenario, "/"),
                datagen_seed=i,
                simulation_output = c("accuracy_summary", "diagnostic_summary"))
    print(paste0("LowFR simulation finished at ", Sys.time(), "."))
    
    hs_sim <- run_sim_horseshoe(scenario=scenario,
                save_output=TRUE,
                #path=paste0("simulations/horseshoe/scenario", scenario, "/"),
                datagen_seed=i,
                simulation_output = c("accuracy_summary", "diagnostic_summary"))
    print(paste0("Horseshoe simulation finished at ", Sys.time(), "."))
    
    fin_sim <- run_sim_FIN(scenario=scenario,
                save_output=TRUE,
                #path=paste0("simulations/FIN/scenario", scenario, "/"),
                datagen_seed=i,
                simulation_output = c("accuracy_summary", "diagnostic_summary"))
    print(paste0("FIN simulation finished at ", Sys.time(), "."))
    
    bkmr_sim <- run_sim_BKMR(scenario=scenario,
                save_output=TRUE,
                #path=paste0("simulations/BKMR/scenario", scenario, "/"),
                datagen_seed=i,
                simulation_output = c("accuracy_summary", "diagnostic_summary"))
    print(paste0("BKMR simulation finished at ", Sys.time(), "."))
    
    bkmr_group_sim <- run_sim_BKMR_group(scenario=scenario,
                save_output=TRUE,
                #path=paste0("simulations/BKMR_group/scenario", scenario, "/"),
                datagen_seed=i,
                simulation_output = c("accuracy_summary", "diagnostic_summary"))
    print(paste0("BKMR_group simulation finished at ", Sys.time(), "."))
    
    cqr_sim <- run_sim_CorrQuadReg(scenario=scenario,
                save_output=TRUE,
                #path=paste0("simulations/CorrQuadReg/scenario", scenario, "/"),
                datagen_seed=i,
                simulation_output = c("accuracy_summary", "diagnostic_summary"))
    print(paste0("CorrQuadReg simulation finished at ", Sys.time(), "."))
    
    end_time <- Sys.time()
    print(paste0("Scenario ", scenario, " seed ", i, " simulations started at ", start_time, " and finished at ", end_time, "."))
    print(paste0("Time elapsed: ", end_time - start_time, "."))
  }
}
```


## Print overall summaries of already-computed results in simulations_results folder


```{r}
# LowFR scenario 1
multi_sim_summary(model="LowFR", scenario=1, seed_list = 1:100, path="simulations_results/")
```

```{r}
# LowFR scenario 2
multi_sim_summary(model="LowFR", scenario=2, seed_list = 1:100, path="simulations_results/")
```

```{r}
# LowFR scenario 3
multi_sim_summary(model="LowFR", scenario=3, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# BKMR scenario 1
multi_sim_summary(model="BKMR", scenario=1, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# BKMR scenario 2
multi_sim_summary(model="BKMR", scenario=2, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# BKMR scenario 3
multi_sim_summary(model="BKMR", scenario=3, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# BKMR_group scenario 1
multi_sim_summary(model="BKMR_group", scenario=1, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# BKMR_group scenario 2
multi_sim_summary(model="BKMR_group", scenario=2, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# BKMR_group scenario 3
multi_sim_summary(model="BKMR_group", scenario=3, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# FIN scenario 1
multi_sim_summary(model="FIN", scenario=1, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# FIN scenario 2
multi_sim_summary(model="FIN", scenario=2, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# FIN scenario 3
multi_sim_summary(model="FIN", scenario=3, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# Horseshoe scenario 1
multi_sim_summary(model="Horseshoe", scenario=1, seed_list = c(1:100), path="simulations_results/")
```


```{r}
# Horseshoe scenario 2
multi_sim_summary(model="Horseshoe", scenario=2, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# Horseshoe scenario 3
multi_sim_summary(model="Horseshoe", scenario=3, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# CorrQuadReg scenario 1
multi_sim_summary(model="CorrQuadReg", scenario=1, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# CorrQuadReg scenario 2
multi_sim_summary(model="CorrQuadReg", scenario=2, seed_list = c(1:100), path="simulations_results/")
```

```{r}
# CorrQuadReg scenario 3
multi_sim_summary(model="CorrQuadReg", scenario=3, seed_list = c(1:100), path="simulations_results/")
```





