---
title: "Summarize simulations for random_seed=1234"
output: pdf_document
date: "2023-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(miceadds)
library(tidyverse)
source.all(path="R")
```

# Simulation visualizations

This notebook makes plots for Section 4 in the paper from already-computed simulations,
which were run with random seed 1234. Since the results needed here include
all posterior samples, the simulations_1234 directory was too large to upload to github.


## Make main effect plots -- Scenario 1
```{r}
model_list <- c("LowFR", "BKMR", "BKMR_group", "FIN", "horseshoe", "CorrQuadReg")
scenario <- 1
y_lim <- c(-1.5, 2.8)
for (model in model_list) {
  print(main_effect_sim_plot(model=model, scenario=scenario, y_lim=y_lim))
}
```

## Make cumulative effect plots -- Scenario 1
```{r}
model_list <- c("LowFR", "BKMR", "BKMR_group", "FIN", "horseshoe", "CorrQuadReg")
scenario <- 1
y_lim <- c(-1, 1.2)
for (model in model_list) {
  print(cum_effect_sim_plot(model=model, scenario=scenario, y_lim=y_lim))
}
```

## Make main effect plots -- Scenario 2
```{r}
model_list <- c("LowFR", "BKMR", "BKMR_group", "FIN", "horseshoe", "CorrQuadReg")
scenario <- 2
y_lim <- c(-1.5, 2.8)
for (model in model_list) {
  print(main_effect_sim_plot(model=model, scenario=scenario, y_lim=y_lim))
}
```

## Make cumulative effect plots -- Scenario 2
```{r}
model_list <- c("LowFR", "BKMR", "BKMR_group", "FIN", "horseshoe", "CorrQuadReg")
scenario <- 2
y_lim <- c(-1.4, 3)
for (model in model_list) {
  print(cum_effect_sim_plot(model=model, scenario=scenario, y_lim=y_lim))
}
```

## Make main effect plots -- Scenario 3
```{r}
model_list <- c("LowFR", "BKMR", "BKMR_group", "FIN", "horseshoe", "CorrQuadReg")
scenario <- 3
y_lim <- c(-1.4, 1.4)
for (model in model_list) {
  print(main_effect_sim_plot(model=model, scenario=scenario, y_lim=y_lim))
}
```

## Make cumulative effect plots -- Scenario 3
```{r}
model_list <- c("LowFR", "BKMR", "BKMR_group", "FIN", "horseshoe", "CorrQuadReg")
scenario <- 3
y_lim <- c(-1.4, 1.4)
for (model in model_list) {
  print(cum_effect_sim_plot(model=model, scenario=scenario, y_lim=y_lim))
}
```

## Selected trace plots -- Scenario 3

```{r}
print(main_effect_traceplot(model="LowFR", scenario=3, Exp=10, t=3, y_lim=c(-0.1,1.6)))
print(main_effect_traceplot(model="BKMR", scenario=3, Exp=10, t=3, y_lim=c(-0.1,1.6)))
print(main_effect_traceplot(model="horseshoe", scenario=3, Exp=10, t=3, y_lim=c(-0.1,1.6)))
```